---
title: "Other_test"
author: "Devashish Patel"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
library(tidyverse)
library(here)
library(ggplot2)
library(readr)
library(skimr)
library(dataReporter)
library(lubridate)
library(tmap)
```


```{r}
df <- read_csv(c("BuildingConditions_2021.csv","BuildingConditions_2020.csv","BuildingConditions_2019.csv","BuildingConditions_2018.csv","BuildingConditions_Aug01-Dec31_2016.csv"))
```


```{r}
df <- df %>% rename(Method_Received = 'Method Received', Created_Date = `Created Date`)
```

Only the columns Block/Address and Street have NA values. If these values are missing then the entire column has no significance as the officials won't know where to go. This is why entire rows have been removed if NA values are present.

```{r}
df <- na.omit(df)
df
```


```{r}
df <- df %>% separate(Created_Date, c("Date","Time"),sep = " ")
View(df)
```


```{r}
df_stats <- df %>% skim
df_stats
```
```{r}
write.csv(df,'BuildingConditions_Compiled.csv')
```


```{r}
df <- read_csv("BuildingConditions_Compiled.csv")
df <- df[,c(2:9),drop = TRUE]
df
```


```{r}
df_sumstats <- summary(df)
df_sumstats
```


```{r}
glimpse(df)
```

```{r}
check(df)
```

As we can see we have used a total of 3 functions namely skim, summary and check to find the respective summary and descriptive stats of the dataset.Since there are no numeric variables in the dataset, we cannot see any numerical statistics.



```{r}
ggplot(df, mapping = aes(x = Method_Received, fill = Ward))+
  geom_bar(position = "dodge")+
  labs(title = "Distribution of Mediums Used to Lodge Building Conditions Complaints")
```


```{r}
ggplot(df,mapping = aes(x = Method_Received, fill = Ward))+
  geom_bar(position = "fill") +
  labs(y = "Proportion", title = "Proportion of Mediums Used to Lodge Building Conditions Complaints")
```


```{r}
df2 <- read_csv(c("BuildingLandImproperUse_2021.csv","BuildingLandImproperUse_2020.csv","BuildingLandImproperUse_2019.csv","BuildingLandImproperUse_2018.csv","BuildingLandImproperUse_Aug01-Dec31_2016.csv"))
```

```{r}
df2 <- df2[,c(1:7),drop = TRUE]
df2
```


```{r}
df2 <- df2 %>% rename(Method_Received = 'Method Received', Created_Date = `Created Date`)
```

Only the columns Block/Address and Street have NA values. If these values are missing then the entire row has no significance as the officials won't know where to go. This is why entire rows have been removed if NA values are present.

```{r}
df2 <- na.omit(df2)
df2
```


```{r}
ggplot(df2, mapping = aes(x = Method_Received, fill = Ward))+
  geom_bar(position = "dodge")+
  labs(title = "Distribution of Mediums used to Lodge Building/Land Improper use Complaints")
```


```{r}
ggplot(df2,mapping = aes(x = Method_Received, fill = Ward))+
  geom_bar(position = "fill") +
  labs(y = "Proportion", title = "Proportion of Mediums used to Lodge Building/Land Improper use Complaints")
```

